### 2020-10-13 introduction.tex

\paragraph*{Contributions and Structure of the Paper}
\begin{itemize}
\item \textbf{Priority GV}: we present Priority GV (PGV) in~\Cref{sec:pgv}; we present the syntax of types and terms, operational semantics and typing rules. We show our type system for PGV is sound by proving subject reduction (\Cref{thm:pgv-subject-reduction-confs}) and closed progress (\Cref{lem:pgv-closed-progress-confs}).
\item \textbf{Milner's Cyclic Scheduler in PGV}: we present for the first time Milner's Cyclic Scheduler \cite{milner89} (\Cref{sec:pgv-example}) as a GV term. This example illustrates how a cyclic structure can now be expressed in PGV thanks to the separation of channel creation and thread creation, and priorities.
\item \textbf{Updated Priority CP}: we present an updated version of Priority CP (PCP) \cite{dardhagay18} in \Cref{sec:pcp} where we remove the commuting conversions and move away from a reduction relation as cycle elimination, and towards a reduction as one would expect for a process calculus. We then show Milner's Cyclic Scheduler in PCP (in \Cref{sec:pcp-example}) originally presented in \cite{dardhagay18}.
\item \textbf{Encoding PCP into PGV}: we present an encoding of PCP into PGV in \Cref{sec:pcp-to-pgv}. We prove the encoding is sound and complete with respect to typing (\Cref{thm:pcp-to-pgv-confs-preservation}) and operational semantics (\Cref{thm:pcp-to-pgv-operational-correspondence-soundness} and \Cref{thm:pcp-to-pgv-operational-correspondence-completeness}). Finally, we can encode Milner's Cyclic Scheduler in PCP (\Cref{sec:pcp-example}) resulting in the Scheduler in PGV (\Cref{sec:pgv-example}).
\end{itemize}
\end{document}

>>>>

\paragraph*{Contributions and Structure of the Paper}
\begin{itemize}
\item \emph{Priority GV} We present Priority GV (PGV) in~\Cref{sec:pgv}; we present the syntax of types and terms, operational semantics and typing rules. We show our type system for PGV is sound by proving subject reduction (\Cref{thm:pgv-subject-reduction-confs}) and closed progress (\Cref{lem:pgv-closed-progress-confs}).
\item \emph{Milner's Cyclic Scheduler in PGV} We present, for the first time, Milner's Cyclic Scheduler \cite{milner89} (\Cref{sec:pgv-example}) as a GV term. This example illustrates how a cyclic structure can now be expressed in PGV thanks to the separation of channel creation and thread creation, and priorities.
\item \emph{Updated Priority CP} We present an updated version of Priority CP (PCP) \cite{dardhagay18} in \Cref{sec:pcp} where we remove the commuting conversions and move away from a reduction relation as cycle elimination, and towards a reduction as one would expect for a process calculus. We then show Milner's Cyclic Scheduler in PCP (in \Cref{sec:pcp-example}) originally presented in \cite{dardhagay18}.
\item \emph{Encoding PCP into PGV} We present an encoding of PCP into PGV in \Cref{sec:pcp-to-pgv}. We prove the encoding is sound and complete with respect to typing (\Cref{thm:pcp-to-pgv-confs-preservation}) and operational semantics (\Cref{thm:pcp-to-pgv-operational-correspondence-soundness} and \Cref{thm:pcp-to-pgv-operational-correspondence-completeness}). Finally, we can encode Milner's Cyclic Scheduler in PCP (\Cref{sec:pcp-example}) resulting in the Scheduler in PGV (\Cref{sec:pgv-example}).
\end{itemize}
\end{document}
